Regime transition identification for basin's governance challenges of water use

### 2020-11-09 tex/main/manuscript.tex
update keywords -gov.
update introduction-section-1 gov.

% 关键词，三到五个
% At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
\keywords{Regime shifts $|$ Sustainability $|$ Instructional fit $|$ Water governance challenges $|$ River basins}

%tag 摘要
% 为了
\begin{abstract}
	\label{abstract}
	% 为了持续的社会经济发展，人类治理了大型河流，并在世界范围内引发了一系列流域尺度的稳态转换。
	For water uses in sustaining socio-economic development, human have governed large rivers and triggered various regime shifts at a basin scale all around the world. 
	% 由于水治理制度决定谁、何时和如何获得水，因此确定其过渡对于指导有效和可持续的用水至关重要。
	Since water governance regime decides who gets what water, when and how, identification for its changes is critical to guiding effective and sustainable water uses.
	% 在这里，考虑到水治理的三个主要维度(压力、供应和分配)，我们开发了一个流域尺度上的综合水治理指数(IWGI)，以检测制度的变化。
	Here, considering three main dimensions of water governance (stress, provision and allocation), we develop an Integrated Water Governance Index (IWGI) at a basin scale to detect regime shifts.
	% 将该指数应用于中国黄河流域，可以看出，在过去半个多世纪中，有三个政权的转变是由经济增长、管理和效率提高引起的。  
	By applying this index to the Yellow River Basin, China, it suggests there were two regimes shifts of water governance throughout half a century, which were caused by changes of environment, economy and policy.
	% 在此基础上，我们总结了一个与水社会循环相对应的一般制度变迁模式。
	Based on the results, we summarized a widespread regime transition schema, corresponding with trajectories of water uses towards hydro-social cycle.
	% 由于资源挑战和结构挑战主要困扰不同制度下的水治理，这一过渡模式可以作为协调大流域治理的有益指导。
	Since resource challenges and structural challenges mainly bother water governance within different regimes, this schema can be a useful guideline for governing big river basins in a coordinated way.
\end{abstract}

@@

\label{introduction}
% tag 引言第一段
% 水资源在人类世的重要性，是支持人类社会发展的基础。
\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for myriad Earth system processes, but also supporting development of human societies in various aspects. 
% TODO 这里增加三篇“大文章”参引
% 但同时, 人类的改造也深刻影响了自然水循环过程, 相关变化可能影响人水系统功能的不利转变，并带来发展困局。
However, human's modification has profoundly influenced the water cycle, which may lead adverse changes to functions of human-water systems, resulting in development dilemmas \cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
% TODO 这里增加参考文献，人类对水循环的改造 
% 大河流域常是经济和文明发展的中心，同时也是面临人类世压力挑战的主要地区，亟需综合水资源治理以实现可持续发展。
Facing major challenges in the Anthropocene, many of the world's big river basins, also hot spots of economy and civilization, urgently need integrated water resources management toward sustainability \cite{bestAnthropogenicStressesWorld2019}. 
% 因此理解人类社会发展与水资源利用的复杂关系，对此有帮助。
Since it requires deep understanding of the complex relationships between human societies and water resources utilization, sketching their transitions provides underlying supports for developing in a coordinated and sustainable way at a basin scales.

% tag 引言第二段
% Regime 和 Regime shift 的定义。
Regime is a stable state of system’s structure and function, whose large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts \cite{rochaCascadingRegimeShifts2018,schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
% 人水系统中的水资源功能
Water have several key functions within a human-water system, the most important of which is sustaining the development of human societies through water utilization. 
% 水资源利用 regime shift
However, interplayed human interference, such as water withdrawal, dam constructions and water managements have significantly changed water functions and induced changes in water use
\cite{falkenmarkUnderstandingWaterResilience2019}.
% 稳态转换随着社会发展增加
These gradual or abrupt changes triggered regime shifts as societies' development strengthen their interlinks to water utilization with increased dependences.
% TODO 这里需要安排参考文献，稳态转换的触发方式，随着社会发展更多
% Regime 过渡性的存在
As a result, most large river basins had gone through phases of accelerated exploitation, over-exploitation, and integrated management, for which it is a reasonable assumption that there is a general transition pattern in water utilization. 
% TODO 这里需要安排参考文献，大河流域的发展历程
% 因此，识别水资源利用的稳态变化，并从中寻找一般性的发展模式，有助于理解流域存在的问题
Identifying the regime shifts in water utilization and sketching a general pattern, therefore, can help to understand and predict developing trajectories of basins, which are crucial for integrated management and coordinated development towards sustainability.

>>>>

% 关键词，三到五个
% At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
\keywords{Regime shifts $|$ Water use $|$ Water governance $|$ Governance challenges $|$ River basins}

%tag 摘要
% 为了
\begin{abstract}
	\label{abstract}
	% 为了持续的社会经济发展，人类治理了大型河流，并在世界范围内引发了一系列流域尺度的稳态转换。
	For water uses in sustaining socio-economic development, human have governed large rivers and triggered various regime shifts at a basin scale all around the world. 
	% 由于水治理制度决定谁、何时和如何获得水，因此确定其过渡对于指导有效和可持续的用水至关重要。
	Since water governance regime decides who gets what water, when and how, identification for its changes is critical to guiding efficient and sustainable water uses.
	% 在这里，考虑到水治理的三个主要维度(压力、供应和分配)，我们开发了一个流域尺度上的综合水治理指数(IWGI)，以检测制度的变化。
	Here, considering three main dimensions of water governance (stress, provision and allocation), we develop an Integrated Water Governance Index (IWGI) at a basin scale to detect regime shifts.
	% 将该指数应用于中国黄河流域，可以看出，在过去半个多世纪中，有三个政权的转变是由经济增长、管理和效率提高引起的。  
	By applying this index to the Yellow River Basin, China, it suggests there were two regimes shifts of water governance throughout half a century, which were caused by changes of environment, economy and policy.
	% 在此基础上，我们总结了一个与水社会循环相对应的一般制度变迁模式。
	Based on the results, we summarized a widespread regime transition schema, corresponding with trajectories of water uses towards hydro-social cycle.
	% 由于资源挑战和结构挑战主要困扰不同制度下的水治理，这一过渡模式可以作为协调大流域治理的有益指导。
	Since resource challenges and structural challenges mainly bother water governance within different regimes, this schema can be a useful guideline for governing big river basins in a coordinated way.
\end{abstract}

@@

\label{introduction-section-1}
% 水资源在人类世的重要性，是支持人类社会发展的基础。
\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for myriad Earth system processes, but also supporting development of human societies in various aspects. 
%* add references
% 然而，根据人类用水的需求，人类的改造对自然水循环产生了深远的影响，并将其发展轨迹逐步推向了水社会循环。
Because of needs for water use, human's modification has profoundly influenced the natural water cycle and led the trajectory toward hydro-social cycle stage by stage
\cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
% 面对人类世世的重大转变，世界许多大河流域，也是经济和文明的热点地区，迫切需要成功的治理以实现可持续发展
Facing this major transformation in the Anthropocene, many of the world's big river basins, also hot spots of economy and civilization, are urgently in need of successful governance for sustainable water use
\cite{bestAnthropogenicStressesWorld2019}. 
% 由于水的治理需要对人类社会和水的使用之间的复杂关系有深刻的理解，因此在流域尺度上，识别由向水-社会水循环的转变所引起的变化是至关重要的。
Since water governance requires deep understanding of the complex relationships between human societies and water use, it is crucial to identify its changes induced by the transformation towards hydro-social water cycle, at a basin scales.

\label{introduction-section-2}
% Regime 和 Regime shift 的定义。
Regime is a stable state of system’s structure and function, of which large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts 
\cite{rochaCascadingRegimeShifts2018,schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
% 人水系统中的水资源功能
Water have several key functions within a human-water system, the most important of which is sustaining the development of human societies through water utilization. 
% 水资源利用 regime shift
However, interplayed human interference, such as water withdrawal, dam constructions and water managements have significantly changed water functions and induced changes in water use
\cite{falkenmarkUnderstandingWaterResilience2019}.
% 稳态转换随着社会发展增加
These gradual or abrupt changes triggered regime shifts as societies' development strengthen their interlinks to water utilization with increased dependences.
% TODO 这里需要安排参考文献，稳态转换的触发方式，随着社会发展更多
% Regime 过渡性的存在
As a result, most large river basins had gone through phases of accelerated exploitation, over-exploitation, and integrated management, for which it is a reasonable assumption that there is a general transition pattern in water utilization. 
% TODO 这里需要安排参考文献，大河流域的发展历程
% 因此，识别水资源利用的稳态变化，并从中寻找一般性的发展模式，有助于理解流域存在的问题
Identifying the regime shifts in water utilization and sketching a general pattern, therefore, can help to understand and predict developing trajectories of basins, which are crucial for integrated management and coordinated development towards sustainability.
